Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-03 paper/paper.tex
use template set of keywords

\providecommand{\keywords}[1]
{
  \small	
  \textbf{\textit{Keywords---}} #1
}

@@

\keywords{Intrusion Detection, Suricata, Rule-based, Synthesis}

% \begin{IEEEkeywords}
%% component, formatting, style, styling, insert
%% \end{IEEEkeywords}

@@

Network Intrusion Detection Systems (\nids{}) are software systems
that monitor the network traffic for malicious behavior and act
accordingly by blocking messages or alerting humans about suspicious
events~\cite{Mitchell:2014:SID:2597757.2542049}. \nids{} are typically
placed behind a firewall, vetting the traffic that the firewall did
not block. Various open-source (\eg{}, Snort~\cite{snort} and
Suricata~\cite{suricata}) and commercial (\eg{},
SolarWinds~\cite{solarwinds} and IBM QRadar~\cite{qradar})
\nids\ implementations exist.

@@

\tname{} takes on input one or more examples of an attack, identified by a domain expert, and produces
on output a ranked list of rules for that attack. One assumption that
we make is that system administrators are able to capture the traffic
that perpetrated the attack. The capture can be obtained by other
institutions, who shared that information, or the organization itself
that suffered the attack and wants to avoid that
repeated. \tname\ uses public data sets of benign
messages~\cite{tcpreplay,stratosphere-normal} and
rulesets~\cite{emerging-threats-open} to create those rules. The
technique is organized as a pipeline of three components. First,
\tname\ uses the messages that manifest an attack to create a
potentially over-specified seed rule. Then, it uses that seed rule and
benign traffic to derive a set of plausible rules that isolate the
benign traffic from the malicious traffic. Finally, it uses existing
rules to learn heuristics to rank the plausible rules.

@@

To sum up, \tname{} uses the messages that manifest an attack in the
first step to create a potentially over-specified seed rule. Then, it
uses benign traffic in the second step to create a set of plausible
rules from the seed rule. Finally, in the third step, \tname{} uses
existing rules to learn heuristics to rank plausible rules.

>>>>

@@

\begin{IEEEkeywords}
Intrusion Detection, Suricata, Rule Synthesis.
\end{IEEEkeywords}

@@

Network Intrusion Detection Systems (\nids{}) are software systems
that monitor the network traffic for malicious behavior and block 
messages or alerting humans about suspicious
events~\cite{Mitchell:2014:SID:2597757.2542049}. \nids{} are typically
placed behind a firewall, vetting the traffic that the firewall did
not block. Various open-source (\eg{}, Snort~\cite{snort},
Suricata~\cite{suricata}) and commercial (\eg{},
SolarWinds~\cite{solarwinds}, IBM QRadar~\cite{qradar})
\nids\ implementations exist.

@@

\tname{} takes on input one or more examples of an attack, identified by a domain expert, and produces
on output a ranked list of rules for that attack. One assumption that
we make is that system administrators are able to capture the traffic
that perpetrated the attack. The capture can be obtained by other
institutions, who shared that information, or the organization itself
that suffered the attack and wants to avoid that
repeated. \tname\ uses public data sets of benign
messages~\cite{tcpreplay,stratosphere-normal} and
rulesets~\cite{emerging-threats-open} to create those rules. The
technique is organized as a pipeline of three components. First,
\tname\ uses the messages that manifest an attack to create a
potentially over-specified seed rule. Then, it uses that seed rule and
benign traffic to derive a set of plausible rules that isolate the
benign traffic from the malicious traffic. Finally, it uses a set of 
heuristics to rank the plausible rules.

@@

To sum up, \tname{} uses the messages that manifest an attack in the
first step to create a potentially over-specified seed rule. Then, it
uses benign traffic in the second step to create a set of plausible
rules from the seed rule. Finally, in the third step, \tname{} uses a 
set of heuristics to rank plausible rules.
